Data Cleaning

### 2025-12-09 Data Cleaning.Rmd
Added multinomial classification.

```{r, include=F}
library(ISLR) ## data package
library(tidyverse) ## data manipulation
library(tidymodels) ## tidy modeling
library(knitr) ## tables
library(rpart.plot) ## tree diagrams
library(vip) ## plotting variable importance
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(zoo)
library(purrr)
library(knitr)
library(patchwork) ## plot arrangement
library(parsnip)
library(discrim)
```

@@

>>>>

```{r, include=F}
library(ISLR) ## data package
library(tidyverse) ## data manipulation
library(tidymodels) ## tidy modeling
library(knitr) ## tables
library(rpart.plot) ## tree diagrams
library(vip) ## plotting variable importance
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(zoo)
library(purrr)
library(knitr)
library(patchwork) ## plot arrangement
library(parsnip)
library(discrim)
library(nnet)
library(broom)
library(dplyr)
library(kableExtra)

@@

## MULTINOMIAL REGRESSION
multi_model <- multinom_reg() |>
  set_engine("nnet") |>
  set_mode("classification")

multi_recipe1 <- recipe(FeCl_change ~ mean_pH + mean_Temp, data = df_train) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors())

multi_recipe <- multi_recipe1

multi_workflow <- workflow() |>
  add_recipe(multi_recipe) |>
  add_model(multi_model)

multi_fit <- fit(multi_workflow, data = df_train)

df_pred_class <- predict(multi_fit, new_data = df_test, type = "class") |>
  bind_cols(df_test |> select(FeCl_change))
df_pred_probs <- predict(multi_fit, new_data = df_test, type = "prob") |>
  bind_cols(df_test |> select(FeCl_change))

accuracy_result <- metrics(df_pred_class, truth = FeCl_change, estimate = .pred_class)
confusion_matrix <- conf_mat(df_pred_class, truth = FeCl_change, estimate = .pred_class)

# results
print(accuracy_result)
print(confusion_matrix)

library(broom)
library(dplyr)
library(knitr)    # For kable()
library(kableExtra) # For extra formatting

# 1. Extract the model fit object
fit_engine <- multi_fit |> extract_fit_engine()

# 2. Tidy the results using the broom package
# The tidy function converts the coefficient matrix into a clean data frame.
tidy_coeffs <- tidy(fit_engine)

# 3. Format the table using kable/kableExtra for display
tidy_coeffs |>
  # Round all numeric columns for cleaner display
  mutate(across(where(is.numeric), ~ round(., 4))) |>

  # Rename columns for clarity (optional, but helpful)
  rename(
    Category = y.level,
    Predictor = term,
    Coefficient = estimate,
    Std_Error = std.error,
    Z_Value = statistic,
    P_Value = p.value
  ) |>

  # Create a nicely formatted Markdown table
  knitr::kable("markdown")
  # OR use kableExtra for more styling options (e.g., HTML/PDF output)
  # kableExtra::kbl(format = "html") |>
  # kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
multi_fit |> extract_fit_engine() |> tibble()
```
